The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-22 Writeup/paper_v3.tex
fig 1 caption tweaking

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2} with best fit
    parameters are plotted over it. The best fit parameters are $a=2.53\pm0.98$, $z1=0.32\pm0.16$, $b=2.70\pm0.50$ and $z2=0.63\pm0.13$.
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Note to self: Give parameter values.}
\rachel{How does this figure look if you show the plot range with the
  histogram going to $z=0$ (still only fitting to $0.3<z<1.25$)?  It
  might be nicer to do that and put a vertical line at $z=0.3$ to
  remind the reader that you only fit above that redshift.} \arun{Done.}
}
  \label{fig:redshift_fluxlimited}
\end{figure}

>>>>

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. The vertical line at $z=0.3$ indicates the delineation between lower redshifts that we do not use for our analysis, and higher redshifts that are used. Fits to two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2}, are also shown, with best-fitting parameters $a=2.53\pm0.98$, $z_1=0.32\pm0.16$, $b=2.70\pm0.50$ and $z_2=0.63\pm0.13$.  We also show the distributions from \protect\cite{2004ApJ...617..765C} from Eqs.~\ref{E;pz3} and~\ref{E;pz4}. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin.
}
  \label{fig:redshift_fluxlimited}
\end{figure}
